---
title: "Bayesian Statistical Models"
subtitle: "Linear Regression, Logistic Regression, Ordered Logit, Count Models, and Beta Models"
format: html
---

##### Load the required packages.

```{r}
library(dplyr) # Data Manipulation
library(ggplot2) # Data Visualization
library(brms) # Bayesian Models
library(rstanarm) # Other Ways to Estimate Bayesian Models
library(marginaleffects) # Estimating Marginal Effects
library(vdemdata) # Data
```

##### Load/Process the data.

```{r}
sub.vdem <- vdem %>%
  # Select Variables of Interest
  select(
    country_id,
    year,
    v2x_polyarchy, # 0-1 Interval Measure of Democracy
    e_v2x_polyarchy_5C, # Ordinal Measure of Democracy
    e_peaveduc, # Count Measure of Average Number of Years of Education Attained (15+)
    e_gdppc, # Continuous Measure of GDP per capita
    e_pop, # Projected Population Size
    e_civil_war # Binary Measure of 1,000+ Battle Deaths
  ) %>%
  # Clean and Create New Variables
  mutate(
    l.gdppc = log(e_gdppc + 1), # Log-Transformed GDP per capita
    l.pop = log(e_pop + 1), # Log-Transformed Population
    democ.bin = ifelse(v2x_polyarchy >= .6, 1, 0), # Democracy Binary Variable
    # Shift the Ordered Democracy Value from {0, 0.25, 0.5, 0.75, 1} to {1, 2, 3, 4, 5}
    e_v2x_polyarchy_5C = case_when(
      e_v2x_polyarchy_5C == 0 ~ 1,
      e_v2x_polyarchy_5C == 0.25 ~ 2,
      e_v2x_polyarchy_5C == 0.5 ~ 3,
      e_v2x_polyarchy_5C == 0.75 ~ 4,
      e_v2x_polyarchy_5C == 1 ~ 5
    )
  ) %>%
  # Rename Variables
  rename(
    democ.index = v2x_polyarchy,
    democ.ord = e_v2x_polyarchy_5C,
    educ = e_peaveduc,
    civ.war = e_civil_war
  )
```

## Linear Regression

##### Optimizing/Specifying Computation

```{r}
lm.chains <- 4
lm.iter <- 2000
lm.warmup <- 1000
lm.cores <- 4
```

##### Specifying Priors of Varying Confidence

```{r}
# Weakly-Informative Priors
lm.wip <- c(
  prior(normal(3.5, 3), class = b, coef = Intercept), # Intercept
  prior(), # Democracy
  prior(normal(6, 4), class = b, coef = l.pop), # Population
  prior(), # Education
  prior(), # Civil War
  prior() # Standard Deviation
)

# Strongly-Informative Priors
lm.sip <- c(
  prior(), # Intercept
  prior(), # Democracy
  prior(), # Population
  prior(), # Education
  prior(), # Civil War
  prior() # Standard Deviation
)
```

##### Notation

##### Estimation {brms}, {rstanarm}, Stan

```{r}
# No Specified Priors

# Non-Informative Priors

# Weakly-Informative Priors

# Strongly-Informative Priors
```

##### Marginal Effect Visualization

##### Bayesian Model Diagnostics

##### Sensitivity Analyses (Priors and Confounding)

##### Power Analysis

## Logistic Regression

##### Optimizing/Specifying Computation

##### Specifying Priors of Varying Confidence

##### Notation

##### Estimation {brms}, {rstanarm}, Stan

##### Marginal Effect Visualization

##### Bayesian Model Diagnostics

##### Sensitivity Analyses (Priors and Confounding)

##### Power Analysis

## Ordered Logistic Regression

##### Optimizing/Specifying Computation

##### Specifying Priors of Varying Confidence

##### Notation

##### Estimation {brms}, {rstanarm}, Stan

##### Marginal Effect Visualization

##### Bayesian Model Diagnostics

##### Sensitivity Analyses (Priors and Confounding)

##### Power Analysis

## Count Models

##### Optimizing/Specifying Computation

##### Specifying Priors of Varying Confidence

##### Notation

##### Estimation {brms}, {rstanarm}, Stan

##### Marginal Effect Visualization

##### Bayesian Model Diagnostics

##### Sensitivity Analyses (Priors and Confounding)

##### Power Analysis

## Beta Regression

##### Optimizing/Specifying Computation

##### Specifying Priors of Varying Confidence

##### Notation

##### Estimation {brms}, {rstanarm}, Stan

##### Marginal Effect Visualization

##### Bayesian Model Diagnostics

##### Sensitivity Analyses (Priors and Confounding)

##### Power Analysis
